---
title: "Analysis"
---

#
## Exploratory Analysis
#### For Analysis of the data, I determined the correlation between percentage of votes cast for each candidate and percentage of each demographic represented in the population by using a technique called linear regression. Linear regression is a statistical analysis technique which can be used to show the correlation between two variables. The regression equation is:

$y = B0 + B1*x$

#### I then found the Intercept, slope, and r-squared value of the regression line using the mean, sd, and cor functions in R. I then graphed the regression lines and used the equations to find if there was a positive, negative, or nonexistent correlation between the demographic data and the election data. This regression would also show if a demographic favored one of the candidates more in one of the elections than the other. If this is the case that could mean the Republican or Democratic candidate did better in targeting those voters in one election than the other. 
#
#### To test whether the results were statistically significance I calculated the p-value of each linear correlation. Significance value = 0.05. If the p-value was less than the significance value then the results were statistically significant and there was a linear relationship between the variables. 
#
```{r Data Input and Manipulation,include=FALSE}
## Final Project Code

# Data
library("readr")
dir = "/Users/mfigaro/Documents/STA 5104 Project/precinctlevelelectionresults2012gen (1)"
setwd(dir)

## 2012 General data
genPrecinct_2012 <- read_csv("2012GenPrecinctCrossReference 2.csv")

# Voting Graphs
library(tidyverse)
library(ggplot2)


# Alachua
ALA_data_2012 <- read_tsv("ALA_PctResults2012GEN.txt",col_names = FALSE)
colnames(ALA_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Brevard
BRE_data_2012 <- read_tsv("BRE_PctResults2012GEN.txt",col_names = FALSE)
colnames(BRE_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Broward
BRO_data_2012 <- read_tsv("BRO_PctResults2012GEN.txt",col_names = FALSE)
colnames(BRO_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Collier
CLL_data_2012 <- read_tsv("CLL_PctResults2012GEN.txt",col_names = FALSE)
colnames(CLL_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Miami-Dade
DAD_data_2012 <- read_tsv("DAD_PctResults2012GEN.txt",col_names = FALSE)
colnames(DAD_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Duval
DUV_data_2012 <- read_tsv("DUV_PctResults2012GEN.txt",col_names = FALSE)
colnames(DUV_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Flagler
FLA_data_2012 <- read_tsv("FLA_PctResults2012GEN.txt",col_names = FALSE)
colnames(FLA_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Hillsborough
HIL_data_2012 <- read_tsv("HIL_PctResults2012GEN.txt",col_names = FALSE)
colnames(HIL_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# INDIAN RIVER
IND_data_2012 <- read_tsv("IND_PctResults2012GEN.txt",col_names = FALSE)
colnames(IND_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Lake
LAK_data_2012 <- read_tsv("LAK_PctResults2012GEN.txt",col_names = FALSE)
colnames(LAK_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# LEE
LEE_data_2012 <- read_tsv("LEE_PctResults2012GEN.txt",col_names = FALSE)
colnames(LEE_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# LEON
LEO_data_2012 <- read_tsv("LEO_PctResults2012GEN.txt",col_names = FALSE)
colnames(LEO_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Manatee
MAN_data_2012 <- read_tsv("MAN_PctResults2012GEN.txt",col_names = FALSE)
colnames(MAN_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Orange
ORA_data_2012 <- read_tsv("ORA_PctResults2012GEN.txt",col_names = FALSE)
colnames(ORA_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Osceola
OSC_data_2012 <- read_tsv("OSC_PctResults2012GEN.txt",col_names = FALSE)
colnames(OSC_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Pinellas
PIN_data_2012 <- read_tsv("PIN_PctResults2012GEN.txt",col_names = FALSE)
colnames(PIN_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Polk
POL_data_2012 <- read_tsv("POL_PctResults2012GEN.txt",col_names = FALSE)
colnames(POL_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Sarasota
SAR_data_2012 <- read_tsv("SAR_PctResults2012GEN.txt",col_names = FALSE)
colnames(SAR_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Seminole
SEM_data_2012 <- read_tsv("SEM_PctResults2012GEN.txt",col_names = FALSE)
colnames(SEM_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# St. Lucie
STL_data_2012 <- read_tsv("STL_PctResults2012GEN.txt",col_names = FALSE)
colnames(STL_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Sumter
SUM_data_2012 <- read_tsv("SUM_PctResults2012GEN.txt",col_names = FALSE)
colnames(SUM_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Volusia
VOL_data_2012 <- read_tsv("VOL_PctResults2012GEN.txt",col_names = FALSE)
colnames(VOL_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Pasco
PAS_data_2012 <- read_tsv("PAS_PctResults2012GEN.txt",col_names = FALSE)
colnames(PAS_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Marion
MRN_data_2012 <- read_tsv("MRN_PctResults2012GEN.txt",col_names = FALSE)
colnames(MRN_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Monroe
MON_data_2012 <- read_tsv("MON_PctResults2012GEN.txt",col_names = FALSE)
colnames(MON_data_2012) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

ALA_data_2012 <- ALA_data_2012 %>% filter(Contest == "President of the United States")
BRE_data_2012 <- BRE_data_2012 %>% filter(Contest == "President of the United States")
BRO_data_2012 <- BRO_data_2012 %>% filter(Contest == "President of the United States")
CLL_data_2012 <- CLL_data_2012 %>% filter(Contest == "President of the United States")
DAD_data_2012 <- DAD_data_2012 %>% filter(Contest == "President of the United States")
DUV_data_2012 <- DUV_data_2012 %>% filter(Contest == "President of the United States")
FLA_data_2012 <- FLA_data_2012 %>% filter(Contest == "President of the United States")
HIL_data_2012 <- HIL_data_2012 %>% filter(Contest == "President of the United States")
IND_data_2012 <- IND_data_2012 %>% filter(Contest == "President of the United States")
LAK_data_2012 <- LAK_data_2012 %>% filter(Contest == "President of the United States")
LEE_data_2012 <- LEE_data_2012 %>% filter(Contest == "President of the United States")
LEO_data_2012 <- LEO_data_2012 %>% filter(Contest == "President of the United States")
MAN_data_2012 <- MAN_data_2012 %>% filter(Contest == "President of the United States")
MON_data_2012 <- MON_data_2012 %>% filter(Contest == "President of the United States")
MRN_data_2012 <- MRN_data_2012 %>% filter(Contest == "President of the United States")
ORA_data_2012 <- ORA_data_2012 %>% filter(Contest == "President of the United States")
OSC_data_2012 <- OSC_data_2012 %>% filter(Contest == "President of the United States")
PAS_data_2012 <- PAS_data_2012 %>% filter(Contest == "President of the United States")
PIN_data_2012 <- PIN_data_2012 %>% filter(Contest == "President of the United States")
POL_data_2012 <- POL_data_2012 %>% filter(Contest == "President of the United States")
SAR_data_2012 <- SAR_data_2012 %>% filter(Contest == "President of the United States")
SEM_data_2012 <- SEM_data_2012 %>% filter(Contest == "President of the United States")
STL_data_2012 <- STL_data_2012 %>% filter(Contest == "President of the United States")
SUM_data_2012 <- SUM_data_2012 %>% filter(Contest == "President of the United States")
VOL_data_2012 <- VOL_data_2012 %>% filter(Contest == "President of the United States")


## 2016 General Data
dir = "/Users/mfigaro/Documents/STA 5104 Project/precinctlevelelectionresults2016gen"
setwd(dir)

# Alachua
ALA_data_2016 <- read_tsv("ALA_PctResults20161108.txt",col_names=FALSE)
colnames(ALA_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Brevard
BRE_data_2016 <- read_tsv("BRE_PctResults20161108.txt",col_names=FALSE)
colnames(BRE_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Broward
BRO_data_2016 <- read_tsv("BRO_PctResults20161108.txt",col_names=FALSE)
colnames(BRO_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Collier
CLL_data_2016 <- read_tsv("CLL_PctResults20161108.txt",col_names=FALSE)
colnames(CLL_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Miami-Dade
DAD_data_2016 <- read_tsv("DAD_PctResults20161108.txt",col_names=FALSE)
colnames(DAD_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Duval
DUV_data_2016 <- read_tsv("DUV_PctResults20161108.txt",col_names=FALSE)
colnames(DUV_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Flagler
FLA_data_2016 <- read_tsv("FLA_PctResults20161108.txt",col_names=FALSE)
colnames(FLA_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Hillsborough
HIL_data_2016 <- read_tsv("HIL_PctResults20161108.txt",col_names=FALSE)
colnames(HIL_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Indian River
IND_data_2016 <- read_tsv("IND_PctResults20161108.txt",col_names=FALSE)
colnames(IND_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Lake
LAK_data_2016 <- read_tsv("LAK_PctResults20161108.txt",col_names=FALSE)
colnames(LAK_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Lee
LEE_data_2016 <- read_tsv("LEE_PctResults20161108.txt",col_names=FALSE)
colnames(LEE_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Leon
LEO_data_2016 <- read_tsv("LEO_PctResults20161108.txt",col_names=FALSE)
colnames(LEO_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Manatee
MAN_data_2016 <- read_tsv("MAN_PctResults20161108.txt",col_names=FALSE)
colnames(MAN_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Orange
ORA_data_2016 <- read_tsv("ORA_PctResults20161108.txt",col_names=FALSE)
colnames(ORA_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Osceola
OSC_data_2016 <- read_tsv("OSC_PctResults20161108.txt",col_names=FALSE)
colnames(OSC_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Pinellas
PIN_data_2016 <- read_tsv("PIN_PctResults20161108.txt",col_names=FALSE)
colnames(PIN_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Polk
POL_data_2016 <- read_tsv("POL_PctResults20161108.txt",col_names=FALSE)
colnames(POL_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Sarasota
SAR_data_2016 <- read_tsv("SAR_PctResults20161108.txt",col_names=FALSE)
colnames(SAR_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

# Seminole
SEM_data_2016 <- read_tsv("SEM_PctResults20161108.txt",col_names=FALSE)
colnames(SEM_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")
# St. Lucie
STL_data_2016 <- read_tsv("STL_PctResults20161108.txt",col_names=FALSE)
colnames(STL_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")
# Sumter
SUM_data_2016 <- read_tsv("SUM_PctResults20161108.txt",col_names=FALSE)
colnames(SUM_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")
# Volusia
VOL_data_2016 <- read_tsv("VOL_PctResults20161108.txt",col_names=FALSE)
colnames(VOL_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")
# Pasco
PAS_data_2016 <- read_tsv("PAS_PctResults20161108.txt",col_names=FALSE)
colnames(PAS_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")
# Marion
MRN_data_2016 <- read_tsv("MRN_PctResults20161108.txt",col_names=FALSE)
colnames(MRN_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")
# Monroe
MON_data_2016 <- read_tsv("MON_PctResults20161108.txt",col_names=FALSE)
colnames(MON_data_2016) = c("Code","Name","ElectionNum","Date","ElectionName",
                            "PrecinctID","PollLocation","TotRegVoters",
                            "RegisteredREP","RegisteredDEM","RegisteredOTHER",
                            "Contest","District","ContestCode","Issue",
                            "CandidateParty","IDNumber","CandidateNum",
                            "VoteTotal")

ALA_data_2016 <- ALA_data_2016 %>% filter(Contest == "President of the United States")
BRE_data_2016 <- BRE_data_2016 %>% filter(Contest == "President of the United States")
BRO_data_2016 <- BRO_data_2016 %>% filter(Contest == "President of the United States")
CLL_data_2016 <- CLL_data_2016 %>% filter(Contest == "President of the United States")
DAD_data_2016 <- DAD_data_2016 %>% filter(Contest == "President of the United States")
DUV_data_2016 <- DUV_data_2016 %>% filter(Contest == "President of the United States")
FLA_data_2016 <- FLA_data_2016 %>% filter(Contest == "President of the United States")
HIL_data_2016 <- HIL_data_2016 %>% filter(Contest == "President of the United States")
IND_data_2016 <- IND_data_2016 %>% filter(Contest == "President of the United States")
LAK_data_2016 <- LAK_data_2016 %>% filter(Contest == "President of the United States")
LEE_data_2016 <- LEE_data_2016 %>% filter(Contest == "President of the United States")
LEO_data_2016 <- LEO_data_2016 %>% filter(Contest == "President of the United States")
MAN_data_2016 <- MAN_data_2016 %>% filter(Contest == "President of the United States")
MON_data_2016 <- MON_data_2016 %>% filter(Contest == "President of the United States")
MRN_data_2016 <- MRN_data_2016 %>% filter(Contest == "President of the United States")
ORA_data_2016 <- ORA_data_2016 %>% filter(Contest == "President of the United States")
OSC_data_2016 <- OSC_data_2016 %>% filter(Contest == "President of the United States")
PAS_data_2016 <- PAS_data_2016 %>% filter(Contest == "President of the United States")
PIN_data_2016 <- PIN_data_2016 %>% filter(Contest == "President of the United States")
POL_data_2016 <- POL_data_2016 %>% filter(Contest == "President of the United States")
SAR_data_2016 <- SAR_data_2016 %>% filter(Contest == "President of the United States")
SEM_data_2016 <- SEM_data_2016 %>% filter(Contest == "PRESIDENT OF THE UNITED STATES")
STL_data_2016 <- STL_data_2016 %>% filter(Contest == "President of the United States")
SUM_data_2016 <- SUM_data_2016 %>% filter(Contest == "President of the United States")
VOL_data_2016 <- VOL_data_2016 %>% filter(Contest == "President of the United States")

# Create frame for bar graph
VoteTotal_data_2012 <- c(sum(ALA_data_2012$VoteTotal), # Alachua
                         sum(BRE_data_2012$VoteTotal), # Brevard
                         sum(BRO_data_2012$VoteTotal), # Broward
                         sum(CLL_data_2012$VoteTotal), # Collier
                         sum(DAD_data_2012$VoteTotal), # Miami-Dade
                         sum(DUV_data_2012$VoteTotal), # Duval
                         sum(FLA_data_2012$VoteTotal), # Flagler
                         sum(HIL_data_2012$VoteTotal), # Hillsborough
                         sum(IND_data_2012$VoteTotal), # Indian River
                         sum(LAK_data_2012$VoteTotal), # Lake
                         sum(LEE_data_2012$VoteTotal), # Lee
                         sum(LEO_data_2012$VoteTotal), # Leon
                         sum(MAN_data_2012$VoteTotal), # Manatee
                         sum(MON_data_2012$VoteTotal), # Monroe
                         sum(MRN_data_2012$VoteTotal), # Marion
                         sum(ORA_data_2012$VoteTotal), # Orange
                         sum(OSC_data_2012$VoteTotal), # Osceola
                         sum(PAS_data_2012$VoteTotal), # Pasco
                         sum(PIN_data_2012$VoteTotal), # Pinellas
                         sum(POL_data_2012$VoteTotal), # Polk
                         sum(SAR_data_2012$VoteTotal), # Sarasota
                         sum(SEM_data_2012$VoteTotal), # Seminole
                         sum(STL_data_2012$VoteTotal), # St. Lucie
                         sum(SUM_data_2012$VoteTotal), # Sumter
                         sum(VOL_data_2012$VoteTotal)) # Volusia

# County Names vector
County_Names <- c("Alachua", "Brevard", "Broward", "Collier","Miami-Dade",
                  "Duval","Flagler","Hillsborough","Indian River","Lake",
                  "Lee","Leon","Manatee","Monroe","Marion","Orange","Osceola",
                  "Paco","Pinellas","Polk","Sarasota","Seminole",
                  "St. Lucie","Sumter","Volusia")

## Votes for each candidate

## 2012
# Republican Votes (Romney / Ryan)
ALA_REPVotes_2012 <- ALA_data_2012 %>% filter(Issue == "Romney / Ryan")
BRE_REPVotes_2012 <- BRE_data_2012 %>% filter(Issue == "Romney / Ryan")
BRO_REPVotes_2012 <- BRO_data_2012 %>% filter(Issue == "Romney / Ryan")
CLL_REPVotes_2012 <- CLL_data_2012 %>% filter(Issue == "Romney / Ryan")
DAD_REPVotes_2012 <- DAD_data_2012 %>% filter(Issue == "Romney / Ryan")
DUV_REPVotes_2012 <- DUV_data_2012 %>% filter(Issue == "Romney / Ryan")
FLA_REPVotes_2012 <- FLA_data_2012 %>% filter(Issue == "Romney / Ryan")
HIL_REPVotes_2012 <- HIL_data_2012 %>% filter(Issue == "Romney / Ryan")
IND_REPVotes_2012 <- IND_data_2012 %>% filter(Issue == "Romney / Ryan")
LAK_REPVotes_2012 <- LAK_data_2012 %>% filter(Issue == "Romney / Ryan")
LEE_REPVotes_2012 <- LEE_data_2012 %>% filter(Issue == "Romney / Ryan")
LEO_REPVotes_2012 <- LEO_data_2012 %>% filter(Issue == "Romney / Ryan")
MAN_REPVotes_2012 <- MAN_data_2012 %>% filter(Issue == "Romney / Ryan")
MON_REPVotes_2012 <- MON_data_2012 %>% filter(Issue == "Romney / Ryan")
MRN_REPVotes_2012 <- MRN_data_2012 %>% filter(Issue == "Romney / Ryan")
ORA_REPVotes_2012 <- ORA_data_2012 %>% filter(Issue == "Romney / Ryan")
OSC_REPVotes_2012 <- OSC_data_2012 %>% filter(Issue == "Romney / Ryan")
PAS_REPVotes_2012 <- PAS_data_2012 %>% filter(Issue == "Romney / Ryan")
PIN_REPVotes_2012 <- PIN_data_2012 %>% filter(Issue == "Romney / Ryan")
POL_REPVotes_2012 <- POL_data_2012 %>% filter(Issue == "Romney / Ryan")
SAR_REPVotes_2012 <- SAR_data_2012 %>% filter(Issue == "Romney / Ryan")
SEM_REPVotes_2012 <- SEM_data_2012 %>% filter(Issue == "Romney / Ryan")
STL_REPVotes_2012 <- STL_data_2012 %>% filter(Issue == "Romney / Ryan")
SUM_REPVotes_2012 <- SUM_data_2012 %>% filter(Issue == "Romney / Ryan")
VOL_REPVotes_2012 <- VOL_data_2012 %>% filter(Issue == "Romney / Ryan")

REPVotes_2012 <- c(sum(ALA_REPVotes_2012$VoteTotal), # Alachua
                         sum(BRE_REPVotes_2012$VoteTotal), # Brevard
                         sum(BRO_REPVotes_2012$VoteTotal), # Broward
                         sum(CLL_REPVotes_2012$VoteTotal), # Collier
                         sum(DAD_REPVotes_2012$VoteTotal), # Miami-Dade
                         sum(DUV_REPVotes_2012$VoteTotal), # Duval
                         sum(FLA_REPVotes_2012$VoteTotal), # Flagler
                         sum(HIL_REPVotes_2012$VoteTotal), # Hillsborough
                         sum(IND_REPVotes_2012$VoteTotal), # Indian River
                         sum(LAK_REPVotes_2012$VoteTotal), # Lake
                         sum(LEE_REPVotes_2012$VoteTotal), # Lee
                         sum(LEO_REPVotes_2012$VoteTotal), # Leon
                         sum(MAN_REPVotes_2012$VoteTotal), # Manatee
                         sum(MON_REPVotes_2012$VoteTotal), # Monroe
                         sum(MRN_REPVotes_2012$VoteTotal), # Marion
                         sum(ORA_REPVotes_2012$VoteTotal), # Orange
                         sum(OSC_REPVotes_2012$VoteTotal), # Osceola
                         sum(PAS_REPVotes_2012$VoteTotal), # Pasco
                         sum(PIN_REPVotes_2012$VoteTotal), # Pinellas
                         sum(POL_REPVotes_2012$VoteTotal), # Polk
                         sum(SAR_REPVotes_2012$VoteTotal), # Sarasota
                         sum(SEM_REPVotes_2012$VoteTotal), # Seminole
                         sum(STL_REPVotes_2012$VoteTotal), # St. Lucie
                         sum(SUM_REPVotes_2012$VoteTotal), # Sumter
                         sum(VOL_REPVotes_2012$VoteTotal)) # Volusia


# Democratic Candidate Votes (Obama / Biden)
ALA_DEMVotes_2012 <- ALA_data_2012 %>% filter(Issue == "Obama / Biden")
BRE_DEMVotes_2012 <- BRE_data_2012 %>% filter(Issue == "Obama / Biden")
BRO_DEMVotes_2012 <- BRO_data_2012 %>% filter(Issue == "Obama / Biden")
CLL_DEMVotes_2012 <- CLL_data_2012 %>% filter(Issue == "Obama / Biden")
DAD_DEMVotes_2012 <- DAD_data_2012 %>% filter(Issue == "Obama / Biden")
DUV_DEMVotes_2012 <- DUV_data_2012 %>% filter(Issue == "Obama / Biden")
FLA_DEMVotes_2012 <- FLA_data_2012 %>% filter(Issue == "Obama / Biden")
HIL_DEMVotes_2012 <- HIL_data_2012 %>% filter(Issue == "Obama / Biden")
IND_DEMVotes_2012 <- IND_data_2012 %>% filter(Issue == "Obama / Biden")
LAK_DEMVotes_2012 <- LAK_data_2012 %>% filter(Issue == "Obama / Biden")
LEE_DEMVotes_2012 <- LEE_data_2012 %>% filter(Issue == "Obama / Biden")
LEO_DEMVotes_2012 <- LEO_data_2012 %>% filter(Issue == "Obama / Biden")
MAN_DEMVotes_2012 <- MAN_data_2012 %>% filter(Issue == "Obama / Biden")
MON_DEMVotes_2012 <- MON_data_2012 %>% filter(Issue == "Obama / Biden")
MRN_DEMVotes_2012 <- MRN_data_2012 %>% filter(Issue == "Obama / Biden")
ORA_DEMVotes_2012 <- ORA_data_2012 %>% filter(Issue == "Obama / Biden")
OSC_DEMVotes_2012 <- OSC_data_2012 %>% filter(Issue == "Obama / Biden")
PAS_DEMVotes_2012 <- PAS_data_2012 %>% filter(Issue == "Obama / Biden")
PIN_DEMVotes_2012 <- PIN_data_2012 %>% filter(Issue == "Obama / Biden")
POL_DEMVotes_2012 <- POL_data_2012 %>% filter(Issue == "Obama / Biden")
SAR_DEMVotes_2012 <- SAR_data_2012 %>% filter(Issue == "Obama / Biden")
SEM_DEMVotes_2012 <- SEM_data_2012 %>% filter(Issue == "Obama / Biden")
STL_DEMVotes_2012 <- STL_data_2012 %>% filter(Issue == "Obama / Biden")
SUM_DEMVotes_2012 <- SUM_data_2012 %>% filter(Issue == "Obama / Biden")
VOL_DEMVotes_2012 <- VOL_data_2012 %>% filter(Issue == "Obama / Biden")

DEMVotes_2012 <- c(sum(ALA_DEMVotes_2012$VoteTotal), # Alachua
                         sum(BRE_DEMVotes_2012$VoteTotal), # Brevard
                         sum(BRO_DEMVotes_2012$VoteTotal), # Broward
                         sum(CLL_DEMVotes_2012$VoteTotal), # Collier
                         sum(DAD_DEMVotes_2012$VoteTotal), # Miami-Dade
                         sum(DUV_DEMVotes_2012$VoteTotal), # Duval
                         sum(FLA_DEMVotes_2012$VoteTotal), # Flagler
                         sum(HIL_DEMVotes_2012$VoteTotal), # Hillsborough
                         sum(IND_DEMVotes_2012$VoteTotal), # Indian River
                         sum(LAK_DEMVotes_2012$VoteTotal), # Lake
                         sum(LEE_DEMVotes_2012$VoteTotal), # Lee
                         sum(LEO_DEMVotes_2012$VoteTotal), # Leon
                         sum(MAN_DEMVotes_2012$VoteTotal), # Manatee
                         sum(MON_DEMVotes_2012$VoteTotal), # Monroe
                         sum(MRN_DEMVotes_2012$VoteTotal), # Marion
                         sum(ORA_DEMVotes_2012$VoteTotal), # Orange
                         sum(OSC_DEMVotes_2012$VoteTotal), # Osceola
                         sum(PAS_DEMVotes_2012$VoteTotal), # Pasco
                         sum(PIN_DEMVotes_2012$VoteTotal), # Pinellas
                         sum(POL_DEMVotes_2012$VoteTotal), # Polk
                         sum(SAR_DEMVotes_2012$VoteTotal), # Sarasota
                         sum(SEM_DEMVotes_2012$VoteTotal), # Seminole
                         sum(STL_DEMVotes_2012$VoteTotal), # St. Lucie
                         sum(SUM_DEMVotes_2012$VoteTotal), # Sumter
                         sum(VOL_DEMVotes_2012$VoteTotal)) # Volusia


## 2016
VoteTotal_data_2016 <- c(sum(ALA_data_2016$VoteTotal), # Alachua
                         sum(BRE_data_2016$VoteTotal), # Brevard
                         sum(BRO_data_2016$VoteTotal), # Broward
                         sum(CLL_data_2016$VoteTotal), # Collier
                         sum(DAD_data_2016$VoteTotal), # Miami-Dade
                         sum(DUV_data_2016$VoteTotal), # Duval
                         sum(FLA_data_2016$VoteTotal), # Flagler
                         sum(HIL_data_2016$VoteTotal), # Hillsborough
                         sum(IND_data_2016$VoteTotal), # Indian River
                         sum(LAK_data_2016$VoteTotal), # Lake
                         sum(LEE_data_2016$VoteTotal), # Lee
                         sum(LEO_data_2016$VoteTotal), # Leon
                         sum(MAN_data_2016$VoteTotal), # Manatee
                         sum(MON_data_2016$VoteTotal), # Monroe
                         sum(MRN_data_2016$VoteTotal), # Marion
                         sum(ORA_data_2016$VoteTotal), # Orange
                         sum(OSC_data_2016$VoteTotal), # Osceola
                         sum(PAS_data_2016$VoteTotal), # Pasco
                         sum(PIN_data_2016$VoteTotal), # Pinellas
                         sum(POL_data_2016$VoteTotal), # Polk
                         sum(SAR_data_2016$VoteTotal), # Sarasota
                         sum(SEM_data_2016$VoteTotal), # Seminole
                         sum(STL_data_2016$VoteTotal), # St. Lucie
                         sum(SUM_data_2016$VoteTotal), # Sumter
                         sum(VOL_data_2016$VoteTotal)) # Volusia

## Votes for each candidate

# Republican Votes (Trump / Pence)
ALA_REPVotes_2016 <- ALA_data_2016 %>% filter(Issue == "Trump / Pence")
BRE_REPVotes_2016 <- BRE_data_2016 %>% filter(Issue == "Trump / Pence")
BRO_REPVotes_2016 <- BRO_data_2016 %>% filter(Issue == "Trump / Pence")
CLL_REPVotes_2016 <- CLL_data_2016 %>% filter(Issue == "Trump / Pence")
DAD_REPVotes_2016 <- DAD_data_2016 %>% filter(Issue == "Trump / Pence")
DUV_REPVotes_2016 <- DUV_data_2016 %>% filter(Issue == "Trump / Pence")
FLA_REPVotes_2016 <- FLA_data_2016 %>% filter(Issue == "Trump / Pence")
HIL_REPVotes_2016 <- HIL_data_2016 %>% filter(Issue == "Trump / Pence")
IND_REPVotes_2016 <- IND_data_2016 %>% filter(Issue == "Trump / Pence")
LAK_REPVotes_2016 <- LAK_data_2016 %>% filter(Issue == "Trump / Pence")
LEE_REPVotes_2016 <- LEE_data_2016 %>% filter(Issue == "Trump / Pence")
LEO_REPVotes_2016 <- LEO_data_2016 %>% filter(Issue == "Trump / Pence")
MAN_REPVotes_2016 <- MAN_data_2016 %>% filter(Issue == "Trump / Pence")
MON_REPVotes_2016 <- MON_data_2016 %>% filter(Issue == "Trump / Pence")
MRN_REPVotes_2016 <- MRN_data_2016 %>% filter(Issue == "Trump / Pence")
ORA_REPVotes_2016 <- ORA_data_2016 %>% filter(Issue == "Trump / Pence")
OSC_REPVotes_2016 <- OSC_data_2016 %>% filter(Issue == "Trump / Pence")
PAS_REPVotes_2016 <- PAS_data_2016 %>% filter(Issue == "Trump / Pence")
PIN_REPVotes_2016 <- PIN_data_2016 %>% filter(Issue == "Trump / Pence")
POL_REPVotes_2016 <- POL_data_2016 %>% filter(Issue == "Trump / Pence")
SAR_REPVotes_2016 <- SAR_data_2016 %>% filter(Issue == "Trump / Pence")
SEM_REPVotes_2016 <- SEM_data_2016 %>% filter(Issue == "Donald J. Trump")
STL_REPVotes_2016 <- STL_data_2016 %>% filter(Issue == "Trump / Pence")
SUM_REPVotes_2016 <- SUM_data_2016 %>% filter(Issue == "Trump / Pence")
VOL_REPVotes_2016 <- VOL_data_2016 %>% filter(Issue == "Trump / Pence")

REPVotes_2016 <- c(sum(ALA_REPVotes_2016$VoteTotal), # Alachua
                         sum(BRE_REPVotes_2016$VoteTotal), # Brevard
                         sum(BRO_REPVotes_2016$VoteTotal), # Broward
                         sum(CLL_REPVotes_2016$VoteTotal), # Collier
                         sum(DAD_REPVotes_2016$VoteTotal), # Miami-Dade
                         sum(DUV_REPVotes_2016$VoteTotal), # Duval
                         sum(FLA_REPVotes_2016$VoteTotal), # Flagler
                         sum(HIL_REPVotes_2016$VoteTotal), # Hillsborough
                         sum(IND_REPVotes_2016$VoteTotal), # Indian River
                         sum(LAK_REPVotes_2016$VoteTotal), # Lake
                         sum(LEE_REPVotes_2016$VoteTotal), # Lee
                         sum(LEO_REPVotes_2016$VoteTotal), # Leon
                         sum(MAN_REPVotes_2016$VoteTotal), # Manatee
                         sum(MON_REPVotes_2016$VoteTotal), # Monroe
                         sum(MRN_REPVotes_2016$VoteTotal), # Marion
                         sum(ORA_REPVotes_2016$VoteTotal), # Orange
                         sum(OSC_REPVotes_2016$VoteTotal), # Osceola
                         sum(PAS_REPVotes_2016$VoteTotal), # Pasco
                         sum(PIN_REPVotes_2016$VoteTotal), # Pinellas
                         sum(POL_REPVotes_2016$VoteTotal), # Polk
                         sum(SAR_REPVotes_2016$VoteTotal), # Sarasota
                         sum(SEM_REPVotes_2016$VoteTotal), # Seminole
                         sum(STL_REPVotes_2016$VoteTotal), # St. Lucie
                         sum(SUM_REPVotes_2016$VoteTotal), # Sumter
                         sum(VOL_REPVotes_2016$VoteTotal)) # Volusia

# Democratic Candidate Votes (Clinton / Kaine)
ALA_DEMVotes_2016 <- ALA_data_2016 %>% filter(Issue == "Clinton / Kaine")
BRE_DEMVotes_2016 <- BRE_data_2016 %>% filter(Issue == "Clinton / Kaine")
BRO_DEMVotes_2016 <- BRO_data_2016 %>% filter(Issue == "Clinton / Kaine")
CLL_DEMVotes_2016 <- CLL_data_2016 %>% filter(Issue == "Clinton / Kaine")
DAD_DEMVotes_2016 <- DAD_data_2016 %>% filter(Issue == "Clinton / Kaine")
DUV_DEMVotes_2016 <- DUV_data_2016 %>% filter(Issue == "Clinton / Kaine")
FLA_DEMVotes_2016 <- FLA_data_2016 %>% filter(Issue == "Clinton / Kaine")
HIL_DEMVotes_2016 <- HIL_data_2016 %>% filter(Issue == "Clinton / Kaine")
IND_DEMVotes_2016 <- IND_data_2016 %>% filter(Issue == "Clinton / Kaine")
LAK_DEMVotes_2016 <- LAK_data_2016 %>% filter(Issue == "Clinton / Kaine")
LEE_DEMVotes_2016 <- LEE_data_2016 %>% filter(Issue == "Clinton / Kaine")
LEO_DEMVotes_2016 <- LEO_data_2016 %>% filter(Issue == "Clinton / Kaine")
MAN_DEMVotes_2016 <- MAN_data_2016 %>% filter(Issue == "Clinton / Kaine")
MON_DEMVotes_2016 <- MON_data_2016 %>% filter(Issue == "Clinton / Kaine")
MRN_DEMVotes_2016 <- MRN_data_2016 %>% filter(Issue == "Clinton / Kaine")
ORA_DEMVotes_2016 <- ORA_data_2016 %>% filter(Issue == "Clinton / Kaine")
OSC_DEMVotes_2016 <- OSC_data_2016 %>% filter(Issue == "Clinton / Kaine")
PAS_DEMVotes_2016 <- PAS_data_2016 %>% filter(Issue == "Clinton / Kaine")
PIN_DEMVotes_2016 <- PIN_data_2016 %>% filter(Issue == "Clinton / Kaine")
POL_DEMVotes_2016 <- POL_data_2016 %>% filter(Issue == "Clinton / Kaine")
SAR_DEMVotes_2016 <- SAR_data_2016 %>% filter(Issue == "Clinton / Kaine")
SEM_DEMVotes_2016 <- SEM_data_2016 %>% filter(Issue == "Hillary R. Clinton")
STL_DEMVotes_2016 <- STL_data_2016 %>% filter(Issue == "Clinton / Kaine")
SUM_DEMVotes_2016 <- SUM_data_2016 %>% filter(Issue == "Clinton / Kaine")
VOL_DEMVotes_2016 <- VOL_data_2016 %>% filter(Issue == "Clinton / Kaine")

DEMVotes_2016 <- c(sum(ALA_DEMVotes_2016$VoteTotal), # Alachua
                         sum(BRE_DEMVotes_2016$VoteTotal), # Brevard
                         sum(BRO_DEMVotes_2016$VoteTotal), # Broward
                         sum(CLL_DEMVotes_2016$VoteTotal), # Collier
                         sum(DAD_DEMVotes_2016$VoteTotal), # Miami-Dade
                         sum(DUV_DEMVotes_2016$VoteTotal), # Duval
                         sum(FLA_DEMVotes_2016$VoteTotal), # Flagler
                         sum(HIL_DEMVotes_2016$VoteTotal), # Hillsborough
                         sum(IND_DEMVotes_2016$VoteTotal), # Indian River
                         sum(LAK_DEMVotes_2016$VoteTotal), # Lake
                         sum(LEE_DEMVotes_2016$VoteTotal), # Lee
                         sum(LEO_DEMVotes_2016$VoteTotal), # Leon
                         sum(MAN_DEMVotes_2016$VoteTotal), # Manatee
                         sum(MON_DEMVotes_2016$VoteTotal), # Monroe
                         sum(MRN_DEMVotes_2016$VoteTotal), # Marion
                         sum(ORA_DEMVotes_2016$VoteTotal), # Orange
                         sum(OSC_DEMVotes_2016$VoteTotal), # Osceola
                         sum(PAS_DEMVotes_2016$VoteTotal), # Pasco
                         sum(PIN_DEMVotes_2016$VoteTotal), # Pinellas
                         sum(POL_DEMVotes_2016$VoteTotal), # Polk
                         sum(SAR_DEMVotes_2016$VoteTotal), # Sarasota
                         sum(SEM_DEMVotes_2016$VoteTotal), # Seminole
                         sum(STL_DEMVotes_2016$VoteTotal), # St. Lucie
                         sum(SUM_DEMVotes_2016$VoteTotal), # Sumter
                         sum(VOL_DEMVotes_2016$VoteTotal)) # Volusia

OtherVotes_2012 <- VoteTotal_data_2012-(REPVotes_2012 + DEMVotes_2012)
OtherVotes_2016 <- VoteTotal_data_2016-(REPVotes_2016 + DEMVotes_2016)
VoteData<-tibble(County_Names,VoteTotal_data_2012,REPVotes_2012,
                 DEMVotes_2012,OtherVotes_2012,VoteTotal_data_2016,REPVotes_2016,
                 DEMVotes_2016,OtherVotes_2016)

## Demographics Data

Pop_data <- data.frame(County = c("Alachua","Alachua","Alachua","Alachua",
                                      "Alachua","Alachua","Alachua","Alachua",
                                      "Alachua","Alachua","Alachua","Alachua",
                                      "Alachua",
                                      "Brevard","Brevard","Brevard","Brevard",
                                      "Brevard","Brevard","Brevard","Brevard",
                                      "Brevard","Brevard","Brevard","Brevard",
                                      "Brevard",
                                      "Broward","Broward","Broward","Broward",
                                      "Broward","Broward","Broward","Broward",
                                      "Broward","Broward","Broward","Broward",
                                      "Broward",
                                      "Collier","Collier","Collier","Collier",
                                      "Collier","Collier","Collier","Collier",
                                      "Collier","Collier","Collier","Collier",
                                      "Collier",
                                      "Miami-Dade","Miami-Dade","Miami-Dade",
                                      "Miami-Dade","Miami-Dade","Miami-Dade",
                                      "Miami-Dade","Miami-Dade","Miami-Dade",
                                      "Miami-Dade","Miami-Dade","Miami-Dade",
                                      "Miami-Dade",
                                      "Duval","Duval","Duval","Duval","Duval",
                                      "Duval","Duval","Duval","Duval","Duval",
                                      "Duval","Duval","Duval",
                                      "Flagler","Flagler","Flagler","Flagler",
                                      "Flagler","Flagler","Flagler","Flagler",
                                      "Flagler","Flagler","Flagler","Flagler",
                                      "Flagler",
                                      "Hillsborough","Hillsborough","Hillsborough",
                                      "Hillsborough","Hillsborough","Hillsborough",
                                      "Hillsborough","Hillsborough","Hillsborough",
                                      "Hillsborough","Hillsborough","Hillsborough",
                                      "Hillsborough",
                                      "Indian River","Indian River","Indian River",
                                      "Indian River","Indian River","Indian River",
                                      "Indian River","Indian River","Indian River",
                                      "Indian River","Indian River","Indian River",
                                      "Indian River",
                                      "Lake","Lake","Lake","Lake","Lake","Lake",
                                      "Lake","Lake","Lake","Lake","Lake","Lake",
                                      "Lake",
                                      "Lee","Lee","Lee","Lee","Lee","Lee","Lee",
                                      "Lee","Lee","Lee","Lee","Lee","Lee",
                                      "Leon","Leon","Leon","Leon","Leon","Leon",
                                      "Leon","Leon","Leon","Leon","Leon","Leon",
                                      "Leon",
                                      "Manatee","Manatee","Manatee","Manatee",
                                      "Manatee","Manatee","Manatee","Manatee",
                                      "Manatee","Manatee","Manatee","Manatee",
                                      "Manatee",
                                      "Monroe","Monroe","Monroe","Monroe",
                                      "Monroe","Monroe","Monroe","Monroe",
                                      "Monroe","Monroe","Monroe","Monroe",
                                      "Monroe",
                                      "Marion","Marion","Marion","Marion",
                                      "Marion","Marion","Marion","Marion",
                                      "Marion","Marion","Marion","Marion",
                                      "Marion",
                                      "Orange","Orange","Orange","Orange",
                                      "Orange","Orange","Orange","Orange",
                                      "Orange","Orange","Orange","Orange",
                                      "Orange",
                                      "Osceola","Osceola","Osceola","Osceola",
                                      "Osceola","Osceola","Osceola","Osceola",
                                      "Osceola","Osceola","Osceola","Osceola",
                                      "Osceola",
                                      "Pasco","Pasco","Pasco","Pasco",
                                      "Pasco","Pasco","Pasco","Pasco",
                                      "Pasco","Pasco","Pasco","Pasco",
                                      "Pasco",
                                      "Pinellas","Pinellas","Pinellas","Pinellas",
                                      "Pinellas","Pinellas","Pinellas","Pinellas",
                                      "Pinellas","Pinellas","Pinellas","Pinellas",
                                      "Pinellas",
                                      "Polk","Polk","Polk","Polk","Polk","Polk",
                                      "Polk","Polk","Polk","Polk","Polk","Polk",
                                      "Polk",
                                      "Sarasota","Sarasota","Sarasota",
                                      "Sarasota","Sarasota","Sarasota",
                                      "Sarasota","Sarasota","Sarasota",
                                      "Sarasota","Sarasota","Sarasota",
                                      "Sarasota",
                                      "Seminole","Seminole","Seminole",
                                      "Seminole","Seminole","Seminole",
                                      "Seminole","Seminole","Seminole",
                                      "Seminole","Seminole","Seminole",
                                      "Seminole",
                                      "St. Lucie","St. Lucie","St. Lucie",
                                      "St. Lucie","St. Lucie","St. Lucie",
                                      "St. Lucie","St. Lucie","St. Lucie",
                                      "St. Lucie","St. Lucie","St. Lucie",
                                      "St. Lucie",
                                      "Sumter","Sumter","Sumter","Sumter",
                                      "Sumter","Sumter","Sumter","Sumter",
                                      "Sumter","Sumter","Sumter","Sumter",
                                      "Sumter",
                                      "Volusia","Volusia","Volusia","Volusia",
                                      "Volusia","Volusia","Volusia","Volusia",
                                      "Volusia","Volusia","Volusia","Volusia",
                                      "Volusia",
                                      "Florida","Florida","Florida","Florida",
                                      "Florida","Florida","Florida","Florida",
                                      "Florida","Florida","Florida","Florida",
                                      "Florida",
                                      "USA","USA","USA","USA","USA","USA",
                                      "USA","USA","USA","USA","USA","USA",
                                      "USA"),
                       Population=c("White alone %","Black %","Native American %",
                                       "Asian %","Pacific Islander alone %",
                                       "Two or more races %", "Latino %",
                                       "White, not Hispanic or Latino %",
                                       "Senior Citizens %","HS Grad %",
                                       "College Grad %", "Population/sq. mi.",
                                       "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop","White alone %","Black %","Native American %",
                                      "Asian %","Pacific Islander alone %",
                                      "Two or more races %", "Latino %",
                                      "White, not Hispanic or Latino %",
                                      "Senior Citizens %","HS Grad %",
                                      "College Grad %", "Population/sq. mi.",
                                      "Total Pop"),
                        Percentage=c(0.699,0.206,0.004,0.062,0.001,0.029,0.105,
                                    0.606,0.146,0.924,0.425,282.7,247336,
                        0.832,0.108,0.005,0.026,0.001,0.028,0.109,
                                    0.738,0.242,0.92,0.293,535,543372,
                        0.631,0.302,0.004,0.039,0.001,0.023,0.311,
                                    0.348,0.171,0.888,0.319,1444.9,1748146,
                        0.893,0.073,0.005,0.016,0.001,0.012,0.286,
                                    0.622,0.329,0.864,0.362,160.9,321522,
                        0.79,0.177,0.003,0.016,0,0.013,0.694,0.129,
                                    0.167,0.815,0.288,1315.5,2497993,
                        0.606,0.308,0.005,0.05,0.001,0.03,0.105,0.52,
                                  0.145,0.895,0.292,1133.9,864253,
                       0.839,0.109,0.004,0.025,0.001,0.023,0.109,
                                   0.744,0.312,0.92,0.244,197.1,95692,
                       0.741,0.18,0.005,0.044,0.001,0.029,0.297,
                                      0.477,0.145,0.884,0.327,1204.9,1229202,
                       0.867,0.096,0.004,0.016,0,0.016,0.127,
                                       0.75,0.338,0.887,0.283,274.5,138028,
                      0.834,0.115,0.006,0.023,0.002,0.021,0.167,0.687,
                                0.271,0.893,0.227,316.6,297047,
                       0.868,0.091,0.005,0.018,0.001,0.017,0.225,0.662,
                               0.292,0.88,0.278,788.7,618755,
                       0.615,0.32,0.003,0.036,0.001,0.024,0.067,0.559,
                                0.139,0.936,0.457,413.1,275483,
                       0.86,0.093,0.005,0.023,0.001,0.019,0.169,0.706,
                                 0.281,0.892,0.293,434.5,322879,
                       0.892,0.071,0.005,0.015,0.001,0.018,0.253,
                                  0.651,0.237,0.913,0.333,74.3,73090,
                       0.821,0.135,0.005,0.017,0.001,0.02,0.141,
                                  0.696,0.292,0.873,0.194,209.1,331299,
                       0.68,0.228,0.006,0.057,0.002,0.028,0.327,0.394,
                                  0.123,0.885,0.338,1268.5,1145957,
                       0.791,0.141,0.008,0.029,0.002,0.029,0.558,
                                   0.301,0.135,0.868,0.205,202.4,268685,
                       0.875,0.067,0.005,0.028,0.001,0.024,0.165,0.727,
                                 0.226,0.89,0.234,622.2,464705,
                       0.825,0.111,0.004,0.036,0.001,0.023,0.102,
                                  0.736,0.254,0.911,0.31,3347.5,916800,
                       0.788,0.162,0.007,0.019,0.001,0.023,0.246,0.569,
                                0.204,0.848,0.2,334.9,602073,
                       0.915,0.047,0.003,0.018,0.001,0.016,0.096,
                                  0.828,0.373,0.928,0.347,682.6,379433,
                       0.786,0.131,0.005,0.05,0.001,0.029,0.225,0.589,
                                  0.16,0.943,0.382,1367,422710,
                       0.736,0.214,0.006,0.02,0.001,0.023,0.199,
                                   0.559,0.247,0.861,0.203,485.7,277255,
                       0.903,0.073,0.004,0.01,0.001,0.01,0.059,0.851,
                                  0.582,0.916,0.311,170.8,93420,
                       0.837,0.115,0.005,0.02,0.001,0.022,0.15,0.706,
                                   0.249,0.9,0.236,449.2,494596,
                       0.773,0.169,0.005,0.03,0.001,0.022,0.264,
                                   0.532,0.209,0.88,0.292,350.6,18804564,
                       0.763,0.134,0.013,0.059,0.002,0.028,0.185,0.601,
                               0.165,0.877,0.315,87.4,308758105))



```

```{r Total Vote Data Bar graphs, include=FALSE}
## Data Vizualization
# Classification for data analysis?
# Hypothesis testing?
library(tidyverse)

# 2012 total vote data bar graph
VoteData_2012<-data.frame(VoteData$County_Names,VoteData$REPVotes_2012,
                          VoteData$DEMVotes_2012,VoteData$OtherVotes_2012)
master_votedata_2012<-VoteData_2012 %>%
  gather("Party","Votes",-VoteData.County_Names)
ElectionResults_2012<-ggplot(data=master_votedata_2012,aes(VoteData.County_Names,Votes))+
  geom_col(aes(fill=as.factor(Party)),position="dodge")+coord_flip()+
  scale_fill_manual(name="Candidate",values=c("blue3","yellow3","red3"),
                    labels=c("Barack Obama and Joe Biden","Other",
                             "Mitt Romney and Paul Ryan"))+
  labs(x="County",y="Total Votes",
       title="Votes by County: 2012 Presidential Election")

# 2016 total vote data bar graph

VoteData_2016<-data.frame(VoteData$County_Names,VoteData$REPVotes_2016,
                          VoteData$DEMVotes_2016,VoteData$OtherVotes_2016)
master_votedata_2016<-VoteData_2016 %>%
  gather("Party","Votes",-VoteData.County_Names)


ElectionResults_2016<-ggplot(data=master_votedata_2016,aes(x=VoteData.County_Names,y=Votes))+
  geom_col(aes(fill=as.factor(Party)),position="dodge")+coord_flip() +
  scale_fill_manual(name="Candidate",values=c("red3","yellow3","blue3"),
                    labels=c("Hillary Clinton and Tim Kaine",
                             "Other",
                             "Donald Trump and Mike Pence"))+
  labs(x="County",y="Total Votes",
       title="Votes by County: 2016 Presidential Election")


## Demographics data (Scatter plots)

# White
Pop_data_white <- Pop_data %>% filter(Population == 
                                        "White, not Hispanic or Latino %")%>%
  summarise(County,Population,"Percentage"=Percentage*100)
avg_white <- Pop_data_white[27,3]
Pop_data_white_county <- Pop_data_white[1:25,]

demog_white_plot<-ggplot(data=Pop_data_white_county,aes(x=County,y=Percentage))+
  geom_point()+geom_hline(yintercept=avg_white,color="red")+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of White People in Each County",
       y="Percentage of Population (%)")

# Black
Pop_data_black <- Pop_data %>% filter(Population == 
                                        "Black %")%>%
  summarise(County,Population,"Percentage"=Percentage*100)
avg_black <- Pop_data_black[27,3]
Pop_data_black_county <- Pop_data_black[1:25,]

demog_black_plot<-ggplot(data=Pop_data_black_county,aes(x=County,y=Percentage))+
  geom_point()+geom_hline(yintercept=avg_black,color="red")+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(y="Percentage of Population (%)",
       title="Percentage of African American People in Each County")

# Native American
Pop_data_na <- Pop_data %>% filter(Population == 
                                        "Native American %")%>%
  summarise(County,Population,"Percentage"=Percentage*100)
avg_na <- Pop_data_na[27,3]
Pop_data_na_county <- Pop_data_na[1:25,]

demog_na_plot<-ggplot(data=Pop_data_na_county,aes(x=County,y=Percentage))+
  geom_point()+geom_hline(yintercept=avg_na,color="red")+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(y="Percentage of Population (%)",
       title="Percentage of Native American People in Each County")

# Asian  
Pop_data_asian <- Pop_data %>% filter(Population == 
                                     "Asian %")%>%
  summarise(County,Population,"Percentage"=Percentage*100)
avg_asian <- Pop_data_asian[27,3]
Pop_data_asian_county <- Pop_data_asian[1:25,]

demog_asian_plot<-ggplot(data=Pop_data_asian_county,aes(x=County,y=Percentage))+
  geom_point()+geom_hline(yintercept=avg_asian,color="red")+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(y="Percentage of Population (%)",
       title="Percentage of Asian People in Each County")

# Pacific Islander
Pop_data_pi <- Pop_data %>% filter(Population == 
                                        "Pacific Islander alone %")%>%
  summarise(County,Population,"Percentage"=Percentage*100)
avg_pi <- Pop_data_pi[27,3]
Pop_data_pi_county <- Pop_data_pi[1:25,]

demog_pi_plot<-ggplot(data=Pop_data_pi_county,aes(x=County,y=Percentage))+
  geom_point()+geom_hline(yintercept=avg_pi,color="red")+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(y="Percentage of Population (%)",
       title="Percentage of Hawaiian/Pacific Islander People in Each County")

# Latino
Pop_data_latino <- Pop_data %>% filter(Population == 
                                        "Latino %")%>%
  summarise(County,Population,"Percentage"=Percentage*100)
avg_latino <- Pop_data_latino[27,3]
Pop_data_latino_county <- Pop_data_latino[1:25,]
demog_latino_plot<-ggplot(data=Pop_data_latino_county,aes(x=County,y=Percentage))+
  geom_point()+geom_hline(yintercept=avg_latino,color="red")+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(y="Percentage of Population (%)",
       title="Percentage of Latino People in Each County")

# Senior Citizens
Pop_data_sc <- Pop_data %>% filter(Population == 
                                        "Senior Citizens %")%>%
  summarise(County,Population,"Percentage"=Percentage*100)
avg_sc <- Pop_data_sc[27,3]
Pop_data_sc_county <- Pop_data_sc[1:25,]

demog_sc_plot<-ggplot(data=Pop_data_sc_county,aes(x=County,y=Percentage))+
  geom_point()+geom_hline(yintercept=avg_sc,color="red")+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(y="Percentage of Population (%)",
       title="Percentage of Senior Citizens in Each County")

## College grads
Pop_data_grad <- Pop_data %>% filter(Population == 
                                        "College Grad %")%>%
  summarise(County,Population,"Percentage"=Percentage*100)
avg_grad <- Pop_data_grad[27,3]
Pop_data_grad_county <- Pop_data_grad[1:25,]

demog_grad_plot<-ggplot(data=Pop_data_grad_county,aes(x=County,y=Percentage))+
  geom_point()+geom_hline(yintercept=avg_grad,color="red")+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(y="Percentage of Population (%)",
       title="Percentage of College Grads in Each County")

## Data Analysis
library(caret)

white_vote_vec <- Pop_data_white_county$Percentage
black_vote_vec <- Pop_data_black_county$Percentage
na_vote_vec <- Pop_data_na_county$Percentage
asian_vote_vec <- Pop_data_asian_county$Percentage
pi_vote_vec <- Pop_data_pi_county$Percentage
latino_vote_vec <- Pop_data_latino_county$Percentage
sc_vote_vec <- Pop_data_sc_county$Percentage
grad_vote_vec <- Pop_data_grad_county$Percentage

```


```{r Data Analysis Regression, echo=FALSE}
# Correlation Regression line

VoteData_2012_master<-VoteData %>% summarise(
  County_Names,
  REPVotes=(REPVotes_2012/VoteData$VoteTotal_data_2012)*100,
  DEMVotes=(DEMVotes_2012/VoteData$VoteTotal_data_2012)*100)

VoteData_2016_master<-VoteData %>% summarise(
  County_Names,
  REPVotes=(REPVotes_2016/VoteTotal_data_2016)*100,
  DEMVotes=(DEMVotes_2016/VoteTotal_data_2016)*100)

REPVotesMaster<-c(VoteData_2012_master$REPVotes,VoteData_2016_master$REPVotes)
DEMVotesMaster<-c(VoteData_2012_master$DEMVotes,VoteData_2016_master$DEMVotes)

white_vote_master<-c(white_vote_vec,white_vote_vec)
black_vote_master<-c(black_vote_vec,black_vote_vec)
na_vote_master <- c(na_vote_vec,na_vote_vec)
asian_vote_master <- c(asian_vote_vec,asian_vote_vec)
pi_vote_master <- c(pi_vote_vec,pi_vote_vec)
latino_vote_master <- c(latino_vote_vec,latino_vote_vec)
sc_vote_master <- c(sc_vote_vec,sc_vote_vec)
grad_vote_master <- c(grad_vote_vec,grad_vote_vec)

VoteData_master<-tibble(REPVotesMaster,DEMVotesMaster,white_vote_master,
                        black_vote_master,na_vote_master,asian_vote_master,
                        pi_vote_master,latino_vote_master,
                        sc_vote_master,grad_vote_master)
VoteData_2012_master<-tibble(VoteData_2012_master,white_vote_vec,black_vote_vec,
                             na_vote_vec,asian_vote_vec,pi_vote_vec,
                             latino_vote_vec,sc_vote_vec,grad_vote_vec)
VoteData_2016_master<-tibble(VoteData_2016_master,white_vote_vec,black_vote_vec,
                             na_vote_vec,asian_vote_vec,pi_vote_vec,
                             latino_vote_vec,sc_vote_vec,grad_vote_vec)

```

```{r,include=FALSE}
## White Voter Regression (REP)
x=VoteData_master$white_vote_master
y=VoteData_master$REPVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r1 <- cor(x,y)
cor.test(x,y)$p.value

w1<-VoteData_master%>% 
  ggplot(aes(white_vote_master, REPVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r1 * s_y/s_x, intercept = m_y - r1 * s_y/s_x * m_x)+
  labs(x="% White Pop",y="REP Votes",title="Both Elections")
c("r","slope","intercept",r1^2,r1*s_y/s_x,m_y - r1 * s_y/s_x * m_x)

#2012
x<-white_vote_vec
y<-VoteData_2012_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r2 <- cor(x,y)
cor.test(x,y)$p.value

w2<-VoteData_2012_master%>% 
  ggplot(aes(white_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r2 * s_y/s_x, intercept = m_y - r2 * s_y/s_x * m_x)+
  labs(x="% White Pop",y="REP Votes",title="2012 Election")
c(r2^2,r2 * s_y/s_x, m_y - r2 * s_y/s_x * m_x)

#2016
x<-white_vote_vec
y<-VoteData_2016_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r3 <- cor(x,y)
cor.test(x,y)$p.value

w3<-VoteData_2016_master%>% 
  ggplot(aes(white_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r3 * s_y/s_x, intercept = m_y - r3 * s_y/s_x * m_x)+
  labs(x="% White Pop",y="REP Votes",title="2016 Election")
c(r3^2,r3 * s_y/s_x, m_y - r3 * s_y/s_x * m_x)

## White Voter Regression (DEM)
x=VoteData_master$white_vote_master
y=VoteData_master$DEMVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r4 <- cor(x,y)
cor.test(x,y)$p.value

w4<-VoteData_master%>% 
  ggplot(aes(white_vote_master, DEMVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r4 * s_y/s_x, intercept = m_y - r4 * s_y/s_x * m_x)+
  labs(x="% White Pop",y="DEM Votes",title="Both Elections")
c(r4^2,r4 * s_y/s_x, m_y - r4 * s_y/s_x * m_x)

#2012
x<-white_vote_vec
y<-VoteData_2012_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r5 <- cor(x,y)
cor.test(x,y)$p.value

w5<-VoteData_2012_master%>% 
  ggplot(aes(white_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r5 * s_y/s_x, intercept = m_y - r5 * s_y/s_x * m_x)+
  labs(x="% White Pop",y="DEM Votes",title="2012 Election")
c(r5^2,r5 * s_y/s_x, m_y - r5 * s_y/s_x * m_x)
#2016
x<-white_vote_vec
y<-VoteData_2016_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r6 <- cor(x,y)
cor.test(x,y)$p.value

w6<-VoteData_2016_master%>% 
  ggplot(aes(white_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r6 * s_y/s_x, intercept = m_y - r6 * s_y/s_x * m_x)+
  labs(x="% White Pop",y="DEM Votes",title="2016 Election")
c(r6^2,r6 * s_y/s_x, m_y - r6 * s_y/s_x * m_x)

library(gridExtra)
```


## Linear Regression of White Population Data
#
#### The Regression Results of White Voter Data showed that the strongest correlation between votes and voters occurred in the 2016 election
```{r echo=FALSE}
grid.arrange(w1,w4,w2,w5,w3,w6)
```

Election Ticket | Regression Equation | R-squared value | P-value
------------- | ----------------------|----------------|-----------
REP 2012 (Romney/Ryan) | y = 0.391x + 26.337 | 0.55731 | 1.822e-05
DEM 2012 (Obama/Biden) | y = -0.391x + 72.154 | 0.570574 | 1.27e-05
REP 2016 (Trump/Pence) | y = 0.494x + 20.037 | 0.65351 | 1.01e-06
DEM 2016 (Clinton/Kaine) | y = -0.495x + 75.146 | 0.68758 | 3.02e-07

#### Counties with larger white populations favored Republican tickets more, and favored Donald Trump in 2016 much more than Mitt Romney in 2012. These results are statistically significant, and there is a correlation between percentage of white people in a county and that county's voting.

```{r echo=FALSE}
vote_corr_white2016 <- tibble(VoteData_2016_master,"white_pop" = white_vote_vec)
  
ggplot(vote_corr_white2016,aes(x=reorder(County_Names,white_pop)))+
  geom_bar(aes(y=REPVotes,color="% REP Votes"),stat="identity")+
  geom_point(aes(y=white_pop,color="% White Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Republican",
                     sec.axis = sec_axis(trans=~./1,name="Percentage White"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Republican Votes vs Percentage White Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")

vote_corr_white2016 <- tibble(VoteData_2016_master,"white_pop" = white_vote_vec)
  
ggplot(vote_corr_white2016,aes(x=reorder(County_Names,white_pop)))+
  geom_bar(aes(y=DEMVotes,color="% DEM Votes"),stat="identity")+
  geom_point(aes(y=white_pop,color="% White Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Democrat",
                     sec.axis = sec_axis(trans=~./1,name="Percentage White"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Democrat Votes vs Percentage White Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")
```



```{r Black Voter Regression,include=FALSE}

## Black Voter Regression (REP)
x=VoteData_master$black_vote_master
y=VoteData_master$REPVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r1 <- cor(x,y)


b1<-VoteData_master%>% 
  ggplot(aes(black_vote_master, REPVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r1 * s_y/s_x, intercept = m_y - r1 * s_y/s_x * m_x)+
  labs(x="% Black Pop",y="REP Votes",title="Both Elections")
c(r1^2,r1 * s_y/s_x, m_y - r1 * s_y/s_x * m_x)

#2012
x<-black_vote_vec
y<-VoteData_2012_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r2 <- cor(x,y)
cor.test(x,y)$p.value

b2<-VoteData_2012_master%>% 
  ggplot(aes(black_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r2 * s_y/s_x, intercept = m_y - r2 * s_y/s_x * m_x)+
  labs(x="% Black Pop",y="REP Votes",title="2012 Election")
c(r2^2,r2 * s_y/s_x, m_y - r2 * s_y/s_x * m_x)

#2016
x<-black_vote_vec
y<-VoteData_2016_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r3 <- cor(x,y)
cor.test(x,y)$p.value

b3<-VoteData_2016_master%>% 
  ggplot(aes(black_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r3 * s_y/s_x, intercept = m_y - r3 * s_y/s_x * m_x)+
  labs(x="% Black Pop",y="REP Votes",title="2016 Election")
c(r3^2,r3 * s_y/s_x, m_y - r3 * s_y/s_x * m_x)

##Black Voter Regression (DEM)
x=VoteData_master$black_vote_master
y=VoteData_master$DEMVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r4 <- cor(x,y)

b4<-VoteData_master%>% 
  ggplot(aes(black_vote_master, DEMVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r4 * s_y/s_x, intercept = m_y - r4 * s_y/s_x * m_x)+
  labs(x="% Black Pop",y="DEM Votes",title="Both Elections")
c(r4^2,r4 * s_y/s_x, m_y - r4 * s_y/s_x * m_x)

#2012
x<-black_vote_vec
y<-VoteData_2012_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r5 <- cor(x,y)
cor.test(x,y)$p.value

b5<-VoteData_2012_master%>% 
  ggplot(aes(black_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r5 * s_y/s_x, intercept = m_y - r5 * s_y/s_x * m_x)+
  labs(x="% Black Pop",y="DEM Votes",title="2012 Election")
c(r5^2,r5 * s_y/s_x, m_y - r5 * s_y/s_x * m_x)

#2016
x<-black_vote_vec
y<-VoteData_2016_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r6 <- cor(x,y)
cor.test(x,y)$p.value

b6<-VoteData_2016_master%>% 
  ggplot(aes(black_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r6 * s_y/s_x, intercept = m_y - r6 * s_y/s_x * m_x)+
  labs(x="% Black Pop",y="DEM Votes",title="2016 Election")
c(r6^2,r6 * s_y/s_x, m_y - r6 * s_y/s_x * m_x)
```

## Linear Regression of Black Population Data
#
#### The Regression Results of Black Voter Data showed that the strongest correlation between votes and voters occurred in the 2016 election
```{r echo=FALSE}
grid.arrange(b1,b4,b2,b5,b3,b6,ncol=2)
```

Election Ticket | Regression Equation | R-squared value | P-value
------------- | ----------------------|----------------|-----------
REP 2012 (Romney/Ryan) | y = -0.783x + 61.524 | 0.46325 | 0.0002
DEM 2012 (Obama/Biden) | y = 0.784x + 36.936 | 0.47609 | 0.0001
REP 2016 (Trump/Pence) | y = -0.958x + 64.028 | 0.51034 | 6.04e-05
DEM 2016 (Clinton/Kaine) | y = 0.948x + 31.236| 0.52304 | 4.42e-05

#### Counties with a larger black population favored the democratic tickets more, and favored Clinton in 2016 more than Obama in 2012.There is a statistically significant linear correlation between percentage of black people in a county and percentage of democrat and republican votes.

```{r echo=FALSE}
vote_corr_black2016 <- tibble(VoteData_2016_master,"black_pop" = black_vote_vec)
  
ggplot(vote_corr_black2016,aes(x=reorder(County_Names,black_pop)))+
  geom_bar(aes(y=REPVotes,color="% REP Votes"),stat="identity")+
  geom_point(aes(y=black_pop,color="% Black Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Republican",
                     sec.axis = sec_axis(trans=~./1,name="Percentage Black"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Republican Votes vs Percentage Black Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")
  
ggplot(vote_corr_black2016,aes(x=reorder(County_Names,black_pop)))+
  geom_bar(aes(y=DEMVotes,color="% DEM Votes"),stat="identity")+
  geom_point(aes(y=black_pop,color="% Black Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Democrat",
                     sec.axis = sec_axis(trans=~./1,name="Percentage Black"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Democrat Votes vs Percentage Black Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")
```


# Linear Regression of Native American Population Data
#
#### There is no significant correlation between Percentage of Native Americans in a County and the percentage vote for each candidate. Their population is too small to make a statistical inference based on it

```{r Native American Regression,include=FALSE}
# Native American Votes Regression (REP)
x=VoteData_master$na_vote_master
y=VoteData_master$REPVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

n1<-VoteData_master%>% 
  ggplot(aes(na_vote_master, REPVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Native American Pop",y="REP Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

# Native American Votes Regression (DEM)
x=VoteData_master$na_vote_master
y=VoteData_master$DEMVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

n2<-VoteData_master%>% 
  ggplot(aes(na_vote_master, DEMVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Native American Pop",y="DEM Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

```

```{r echo=FALSE}
grid.arrange(n1,n2,ncol=2)
```

Party Ticket (2012 and 2016) | Regression Equation | R-squared value | P-value
------------- | ----------------------|----------------|----------
REP | y = 2.968x + 48.553 | 0.0012981 | 0.804
DEM | y = -3.243x + 48.379 | 0.001558 | 0.786

#
#### There is no statistically significant correlation between Percentage of Native Americans in a County and the percentage vote for each candidate.
#
#
## Linear Regression of Pacific Islander Population Data

```{r Pacific Islander Regression, include=FALSE}

#Pacific Islander Regresssion (REP)
x=VoteData_master$pi_vote_master
y=VoteData_master$REPVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

p1<-VoteData_master%>% 
  ggplot(aes(pi_vote_master, REPVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Pacific Islander Pop",y="REP Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#Pacific Islander Regresssion (DEM)
x=VoteData_master$pi_vote_master
y=VoteData_master$DEMVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

p2<-VoteData_master%>% 
  ggplot(aes(pi_vote_master, DEMVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Pacific Islander Pop",y="DEM Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

```

```{r echo=FALSE}
grid.arrange(p1,p2,ncol=2)
```

Party Ticket (2012 and 2016) | Regression Equation | R-squared value | P-value
------------- | ----------------------|----------------|--------------
REP | y = -27.827x + 52.884 | 0.016961 | 0.367
DEM | y = 24.488x + 44.262 | 0.013209 | 0.427

#
#### There is no statistically significant correlation between Percentage of Hawaiians or Pacific Islanders in a County and the percentage vote for each candidate. Their population is too small to make a statistical inference based on it
#
## Linear Regression of Asian Population Data

```{r Asian Votes Regression,include=FALSE}
#Asian Votes Regression (REP)
x=VoteData_master$asian_vote_master
y=VoteData_master$REPVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)

a1<-VoteData_master%>% 
  ggplot(aes(asian_vote_master, REPVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Asian Pop",y="REP Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2012
x<-asian_vote_vec
y<-VoteData_2012_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

a2<-VoteData_2012_master%>% 
  ggplot(aes(asian_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Asian Pop",y="REP Votes",title="2012 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2016
x<-asian_vote_vec
y<-VoteData_2016_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

a3<-VoteData_2016_master%>% 
  ggplot(aes(asian_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Asian Pop",y="REP Votes",title="2016 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#Asian Voter Regression (DEM)
x=VoteData_master$asian_vote_master
y=VoteData_master$DEMVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)

a4<-VoteData_master%>% 
  ggplot(aes(asian_vote_master, DEMVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Asian Pop",y="DEM Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2012
x<-asian_vote_vec
y<-VoteData_2012_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

a5<-VoteData_2012_master%>% 
  ggplot(aes(asian_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Asian Pop",y="REP Votes",title="2012 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2016
x<-asian_vote_vec
y<-VoteData_2016_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

a6<-VoteData_2016_master%>% 
  ggplot(aes(asian_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Asian Pop",y="DEM Votes",title="2016 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)
```
#### The Regression Results of Asian Voter Data showed that the strongest correlation between votes and voters occurred in the 2016 election
#
```{r echo=FALSE}
grid.arrange(a1,a4,a2,a5,a3,a6,ncol=2)
```

Election Ticket | Regression Equation | R-squared value | P-value
------------- | ----------------------|----------------|------------
REP 2012 (Romney/Ryan) | y = -3.284x + 59.393 | 0.28008 | 0.0065
DEM 2012 (Obama/Biden) | y = 3.207x + 39.313 | 0.27325 | 0.0073
REP 2016 (Trump/Pence) | y = -4.518x + 62.839 | 0.38962 | 0.00085
DEM 2016 (Clinton/Kaine) | y = 4.169x + 33.27| 0.347397 | 0.00193

#
```{r echo=FALSE}
vote_corr_asian2016 <- tibble(VoteData_2016_master,"asian_pop" = asian_vote_vec)
  
ggplot(vote_corr_asian2016,aes(x=reorder(County_Names,asian_pop)))+
  geom_bar(aes(y=REPVotes,color="% REP Votes"),stat="identity")+
  geom_point(aes(y=asian_pop,color="% Asian Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Republican",
                     sec.axis = sec_axis(trans=~./1,name="Percentage Asian"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Republican Votes vs Percentage Asian Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")
  
ggplot(vote_corr_asian2016,aes(x=reorder(County_Names,asian_pop)))+
  geom_bar(aes(y=DEMVotes,color="% DEM Votes"),stat="identity")+
  geom_point(aes(y=asian_pop,color="% Asian Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Democrat",
                     sec.axis = sec_axis(trans=~./1,name="Percentage Asian"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Democrat Votes vs Percentage Asian Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")
```

## Linear Regression of Latino Population Data
```{r Latino Voter Regression,include=FALSE}
#Latino Voter Regression (REP)
x=VoteData_master$latino_vote_master
y=VoteData_master$REPVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)

l1<-VoteData_master%>% 
  ggplot(aes(latino_vote_master, REPVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="REP Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2012
x<-latino_vote_vec
y<-VoteData_2012_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

l2<-VoteData_2012_master%>% 
  ggplot(aes(latino_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="REP Votes",title="2012 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2016
x<-latino_vote_vec
y<-VoteData_2016_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

l3<-VoteData_2016_master%>% 
  ggplot(aes(latino_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="REP Votes",title="2016 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#Latino Voter Regression (DEM)
x=VoteData_master$latino_vote_master
y=VoteData_master$DEMVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)

l4<-VoteData_master%>% 
  ggplot(aes(latino_vote_master, DEMVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="DEM Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2012
x<-latino_vote_vec
y<-VoteData_2012_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

l5<-VoteData_2012_master%>% 
  ggplot(aes(latino_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="DEM Votes",title="2012 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2016
x<-latino_vote_vec
y<-VoteData_2016_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

l6<-VoteData_2016_master%>% 
  ggplot(aes(latino_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="DEM Votes",title="2016 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

```

```{r echo=FALSE}
grid.arrange(l1,l4,l2,l5,l3,l6,ncol=2)
```
#### The Regression Results of Latino Voter Data showed that the strongest correlation between votes and voters occurred in the 2016 election
#

Election Ticket | Regression Equation | R-squared value | P-value
------------- | ----------------------|----------------|-----------
REP 2012 (Romney/Ryan) | y = -0.288x + 56.128 | 0.22838 | 0.0157
DEM 2012 (Obama/Biden) | y = 0.289x + 42.341 | 0.234903 | 0.0141
REP 2016 (Trump/Pence) | y = -0.370x + 57.780 | 0.27620 | 0.00698
DEM 2016 (Clinton/Kaine) | y = 0.379x + 37.145| 0.30333 | 0.00433

#
#### Counties with more Latino residents broke more strongly for Clinton in 2016 than for Obama in 2012 but not by a large margin. There is a statistically significant linear correlation between these variables in both elections.
#
```{r echo=FALSE}
vote_corr_latino2016 <- tibble(VoteData_2016_master,"latino_pop" = latino_vote_vec)
  
ggplot(vote_corr_latino2016,aes(x=reorder(County_Names,latino_pop)))+
  geom_bar(aes(y=REPVotes,color="% REP Votes"),stat="identity")+
  geom_point(aes(y=latino_pop,color="% Latino Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Republican",
                     sec.axis = sec_axis(trans=~./1,name="Percentage Latino"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Republican Votes vs Percentage Latino Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")
  
ggplot(vote_corr_latino2016,aes(x=reorder(County_Names,latino_pop)))+
  geom_bar(aes(y=DEMVotes,color="% DEM Votes"),stat="identity")+
  geom_point(aes(y=latino_pop,color="% Latino Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Democrat",
                     sec.axis = sec_axis(trans=~./1,name="Percentage Latino"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Democrat Votes vs Percentage Latino Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")
```


## Linear Regression of Senior Citizen Population Data
```{r,include=FALSE}
#Senior Citizen Voter Regression (REP)

x=VoteData_master$sc_vote_master
y=VoteData_master$REPVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)

s1<-VoteData_master%>% 
  ggplot(aes(sc_vote_master, REPVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Senior Citizen Pop",y="REP Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2012
x<-sc_vote_vec
y<-VoteData_2012_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

s2<-VoteData_2012_master%>% 
  ggplot(aes(sc_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="REP Votes",title="2012 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2016
x<-sc_vote_vec
y<-VoteData_2016_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

s3<-VoteData_2016_master%>% 
  ggplot(aes(sc_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="REP Votes",title="2012 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#Senior Citizen Regression (DEM)
x=VoteData_master$sc_vote_master
y=VoteData_master$DEMVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)

s4<-VoteData_master%>% 
  ggplot(aes(sc_vote_master, DEMVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Senior Citizen Pop",y="DEM Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2012
x<-sc_vote_vec
y<-VoteData_2012_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

s5<-VoteData_2012_master%>% 
  ggplot(aes(sc_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="DEM Votes",title="2012 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2016
x<-sc_vote_vec
y<-VoteData_2016_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

s6<-VoteData_2016_master%>% 
  ggplot(aes(sc_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% Latino Pop",y="DEM Votes",title="2016 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)
```


```{r echo=FALSE}
grid.arrange(s1,s4,s2,s5,s3,s6,ncol=2)
```


#

Election Ticket | Regression Equation | R-squared value | P-value
------------- | ----------------------|----------------|------------
REP 2012 (Romney/Ryan) | y = 0.678x + 33.584 | 0.58837 | 7.708e-06
DEM 2012 (Obama/Biden) | y = -0.666x + 64.594 | 0.57978 | 9.838e-06
REP 2016 (Trump/Pence) | y = 0.810x + 30.325 | 0.61653 | 3.342e-06
DEM 2016 (Clinton/Kaine) | y = -0.763x + 63.647| 0.57276 | 1.197e-05

#
#### The Regression Results of Senior Citizen Voter Data showed that the strongest correlation between votes and voters occurred in the 2016 election. Also, elderly voters broke much harder for Trump in 2016 than they did for Romney in 2012, as evidenced by the stronger and significantly more positive linear correlation in 2016. There is a statistically significant linear correlation between these variables.

```{r echo=FALSE}
vote_corr_sc2016 <- tibble(VoteData_2016_master,"sc_pop" = sc_vote_vec)
  
ggplot(vote_corr_sc2016,aes(x=reorder(County_Names,sc_pop)))+
  geom_bar(aes(y=REPVotes,color="% REP Votes"),stat="identity")+
  geom_point(aes(y=sc_pop,color="% Senior Citizen Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Republican",
                     sec.axis = sec_axis(trans=~./1,name="Percentage Senior Citizen"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Republican Votes vs Percentage Senior Citizen Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")
  
ggplot(vote_corr_sc2016,aes(x=reorder(County_Names,sc_pop)))+
  geom_bar(aes(y=DEMVotes,color="% DEM Votes"),stat="identity")+
  geom_point(aes(y=sc_pop,color="% Senior Citizen Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Democrat",
                     sec.axis = sec_axis(trans=~./1,name="Percentage Senior Citizen"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Democrat Votes vs Percentage Senior Citizen Voters 2016",
       x="Counties")+scale_color_discrete(name="Legend")
```

## Linear Regression of College Graduate Population Data

```{r,include=FALSE}
# College Grad Regression (REP)
x=VoteData_master$grad_vote_master
y=VoteData_master$REPVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)

g1<-VoteData_master%>% 
  ggplot(aes(grad_vote_master, REPVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% College Grad Pop",y="REP Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2012
x<-grad_vote_vec
y<-VoteData_2012_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

g2<-VoteData_2012_master%>% 
  ggplot(aes(grad_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% College Grad Pop",y="REP Votes",title="2012 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2016
x<-grad_vote_vec
y<-VoteData_2016_master$REPVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

g3<-VoteData_2016_master%>% 
  ggplot(aes(grad_vote_vec, REPVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% College Grad Pop",y="REP Votes",title="2016 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

# College Grad Regression (DEM)
x=VoteData_master$grad_vote_master
y=VoteData_master$DEMVotesMaster

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)

g4<-VoteData_master%>% 
  ggplot(aes(grad_vote_master, DEMVotesMaster)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% College Grad Pop",y="DEM Votes",title="Both Elections")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2012
x<-grad_vote_vec
y<-VoteData_2012_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

g5<-VoteData_2012_master%>% 
  ggplot(aes(grad_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% College Grad Pop",y="DEM Votes",title="2012 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)

#2016
x<-grad_vote_vec
y<-VoteData_2016_master$DEMVotes

m_x <- mean(x)
m_y <- mean(y)
s_x <- sd(x)
s_y <- sd(y)
r <- cor(x,y)
cor.test(x,y)$p.value

g6<-VoteData_2016_master%>% 
  ggplot(aes(grad_vote_vec, DEMVotes)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = r * s_y/s_x, intercept = m_y - r * s_y/s_x * m_x)+
  labs(x="% College Grad Pop",y="DEM Votes",title="2016 Election")
c(r^2,r * s_y/s_x,m_y - r * s_y/s_x * m_x)
```


```{r echo=FALSE}
grid.arrange(g1,g4,g2,g5,g3,g6,ncol=2)
```


Election Ticket | Regression Equation | R-squared value | P-value
------------- | ----------------------|----------------|-----------
REP 2012 (Romney/Ryan) | y = -0.278x + 58.227 | 0.04584 | 0.304
DEM 2012 (Obama/Biden) | y = 0.274x + 40.380 | 0.045523 | 0.0553
REP 2016 (Trump/Pence) | y = -0.587x + 67.290 | 0.15058 | 0.3058
DEM 2016 (Clinton/Kaine) | y = 0.529x + 29.543| 0.12798 | 0.079

#### The Regression Results of College Graduate Voter Data showed that the correlation between percentage college graguates and percentage DEM and REP votes was not statistically significant.
#

```{r echo=FALSE}
vote_corr_grad2016 <- tibble(VoteData_2016_master,"grad_pop" = grad_vote_vec)
  
ggplot(vote_corr_grad2016,aes(x=reorder(County_Names,grad_pop)))+
  geom_bar(aes(y=REPVotes,color="% REP Votes"),stat="identity")+
  geom_point(aes(y=grad_pop,color="% College Grad Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Republican",
                     sec.axis = sec_axis(trans=~./1,name="Percentage College Grad"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Republican Votes vs Percentage College Graduates 2016",
       x="Counties")+scale_color_discrete(name="Legend")
  
ggplot(vote_corr_grad2016,aes(x=reorder(County_Names,grad_pop)))+
  geom_bar(aes(y=DEMVotes,color="% DEM Votes"),stat="identity")+
  geom_point(aes(y=grad_pop,color="% College Grad Pop"),stat="identity")+
  scale_y_continuous(name="Percentage Democrat",
                     sec.axis = sec_axis(trans=~./1,name="Percentage Senior Citizen"))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  labs(title="Percentage of Democrat Votes vs Percentage College Graduates 2016",
       x="Counties")+scale_color_discrete(name="Legend")
```


# Conclusion
#

The data found that there was a significant correlation between demographics data and voting. The demographics data that had the most significant correlation with an increase in voting were Black Voters and Senior Citizen Voters. Both of these demographics also broke more strongly towards their favored parties in the 2016 elections. Counties with more senior citizens trended more heavily towards Donald Trump than Mitt Romney, and counties with black voters trended more heavily towards Hillary Clinton than Barack Obama. I deduced this because the slopes for the 2016 linear regression equations were larger, meaning the votes trended more heavily towards one party when that population demographic increased. This difference in data was likely due to the difference in candidates. Donald Trump was a candidate that appealed to conservative values with his motto "Make America Great Again." These ideas are likely what appealed most to Elderly voters. Counties with black voters, despite the running of the first black president for reelection, appeared to favor Hillary Clinton more by percentage. This could be due to their mistrust of Donald Trump due to his many controversial and inflammatory comments, or inacurracies in the model that will be discussed later.

Another surprising result of this model is the apparent lack of correlation between a county's Latino population and how that county voted, despite how large the Latino population is in Florida. This is likely due to the fact that Latinos encompass a large variety of people from different countries and regions. The term "latinos" is a very general term that could encompass people from Mexico, Cuba, Puerto Rico, Central America, and South America. Attempting to predict how these people will vote is therefore quite difficult, and pollsters should redefine the term in the future. Surprisingly, there was no statistically significant correlation between percentage college graduates in a county and how that county voted. This became an important distinction between Democratic and Republican voters in future elections, but this was not significant in the observed counties in Florida. If I were to redo this project, I would include more rural Florida counties to observe how class and education influenced these elections.

Some of the weaknesses of this model include the number of counties. Including more counties would enable me to show a greater correlation between demographics and voting choice. Also, it is difficult to say which demographic had the greatest effect on the election's outcome in each county. You could say the largest proportion had the greatest effect, but there are several factors that influence voting, including economic standing age, and population density. Just because a county like Miami-Dade and Broward may have a greater number of Latino and back residents than white residents, impoverished minority communities often experience a lower voter turnout than affluent white communities due to gaps in education, class, and population density. Urban, inner-city, residents of Florida's largest cities can often experience very long wait times due to the large population density and limited polling places. 

Overall, this model had the expected results for each demographic based on typical polls and election results. However, it could have been built to show a more accurate depiction of the relationship between demographics and voting. Including more counties or more elections would have benefited the model greatly. This was a generally insightful and interesting project to develop, and this method of analyzing voters using the concepts of data anlysis and vizualization could be very helpful to pollsters and campaigns in the future. Lastly, the 2016 Election displayed stronger correlations in every case, along with voters from each demographic favoring the party they did in 2016 much more strongly. This tendency, for example, of counties with high percentages of white people to vote in higher numbers for the republican candidate in 2016, Donald Trump, portrays a significant divide developing in the American people, between people of different race, age, and economic standing. It is my hope that utilizing data techniques such as this model will notify candidates and parties of this growing divide, and that it will convince them not to worsen it by catering to their base, but to bring Americans together through bipartisan politics and cooperation.

### Sources

Voting Data: https://dos.myflorida.com/elections/data-statistics/elections-data/precinct-level-election-results/

#

Demographics Data: https://www.census.gov/quickfacts/fact/table/FL,US/RHI125219

#

White house photo: https://www.whitehouse.gov/get-involved/

#

Florida map photo: https://www.bbc.com/news/election-us-2016-37889032

